\pointlike's MC Simulation Package

### 2012-06-27 presentations/lande_roi_monte_carlo_simulation_wg_june_27_2012/lande_roi_monte_carlo_simulation_wg_june_27_2012.tex
update talk

\begin{frame}{Motivation (Ext. Srs. Search paper)}
\begin{columns}
  \column{.4\textwidth} 
  \includegraphics[scale=0.4]{plots/ext_src_table.pdf}
  \column{.6\textwidth} 
  \includegraphics[scale=0.45]{plots/ext_src_plot.pdf}

@@

\begin{frame}{\pointlike's MC Simulation package}
  \begin{itemize}
    \item I developed a wrapper around \gtobssim to automate
      otherwise time consuming, tedious, or error-prone tasks
    \item Built around \pointlike, an alternate maximum
      likelihood package written in \python
      \begin{itemize}
      \item Uses as input a list of \pointlike objects
        \item Builds the XML file for \gtobssim
        \item Converts unsupported models into required templates.
        \item Automatically removes bad time intervals + \texttt{zmax} cut
      \end{itemize}
    \item Code is in \pointlike package: \texttt{uw.like.roi\_monte\_carlo.py}.
    \item \url{http://www-glast.stanford.edu/cgi-bin/viewcvs/pointlike/python/uw/like/roi_monte_carlo.py}
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item \gtobssim supports power law, (dark matter) line, broken powerlaw
  \begin{itemize}
    \item \url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/other_sources.html}
  \end{itemize}
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item Requires generating a 2D data file of spectral model
    \item \roimc will use \pointlike automatically build the \texttt{FileSpectrum} 
    \item \gtobssim Requires integral of spectral model (done automatically by \roimc)
    \item WARNING! \texttt{FileSpectrum} objects cannot contain 0 pixels (stripped out by \roimc)
  \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]
  \frametitle{Common Gotcha's (Energy Dispersion)}
  \begin{itemize}
        \item Energy dispersion means photons with energies outside simulation range can
          disperse into simulation
          \begin{itemize}
            \item All spectral models must be simulated for energies well outside simulation range!
          \end{itemize}
        \item Handled automatically by \roimc. 
          \begin{itemize}
            \item Parameter \texttt{roi\_pad} (default=2) will pad a given
              amount to energy to every spectral models.
          \end{itemize}
      \end{itemize}
\begin{lstlisting}[language=Python]
actual_emin = simulation_emin/roi_pad
actual_emax = simulation_emax*roi_pad
\end{lstlisting}
\end{frame}

>>>>

\begin{frame}{Motivation (Ext. Srs. Search paper)}
\begin{columns}
  \column{.5\textwidth} 
  \includegraphics[scale=0.35]{plots/bias_w44sim_color.pdf}

  \begin{itemize}
    \item Simulation of W44 + Galactic \& Isotropic Diffuse $\sim 1,000$ times
  \end{itemize}

  \column{.5\textwidth} 
  \includegraphics[scale=0.35]{plots/ts_comparison_w44sim_color.pdf}

  \begin{itemize}
    \item Look at distribution of TS values fitting with different spatial models
  \end{itemize}
\end{columns}

\begin{frame}{Ext. Srs. Search paper (cont)}
\begin{columns}
  \column{.4\textwidth} 
  \includegraphics[scale=0.4]{plots/ext_src_table.pdf}
  \column{.6\textwidth} 
  \includegraphics[scale=0.45]{plots/ext_src_plot.pdf}

@@

\begin{frame}{\pointlike's MC Simulation package}
  \begin{itemize}
    \item I developed a wrapper around \gtobssim to automate
      otherwise time consuming, tedious, or error-prone tasks
    \item Built around \pointlike, an alternate maximum
      likelihood package written in \python
      \begin{itemize}
      \item Uses as input a list of \pointlike sources
        \item Builds the XML file for \gtobssim
        \item Converts unsupported models into required templates.
        \item Automatically removes bad time intervals + \texttt{zmax} cut
      \end{itemize}
    \item Code is in \pointlike package: \texttt{uw.like.roi\_monte\_carlo.py}.
    \item \url{http://www-glast.stanford.edu/cgi-bin/viewcvs/pointlike/python/uw/like/roi_monte_carlo.py}
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item \gtobssim supports power law, (dark matter) line, broken powerlaw
  \begin{itemize}
    \item \url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/other_sources.html}
  \end{itemize}
\item No LogParabola, ExpCutoff\dots
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item Requires generating a 1D data file of spectral model
    \item \roimc uses \pointlike to automatically build the \texttt{FileSpectrum} 
    \item \gtobssim requires integral of spectral model (done automatically by \roimc)
    \item WARNING! \texttt{FileSpectrum} objects cannot contain 0 pixels (stripped out by \roimc)
  \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]
  \frametitle{Common Gotcha's (Energy Dispersion)}
  \begin{itemize}
        \item Energy dispersion means photons with energies outside simulation range can
          disperse into simulation
          \begin{itemize}
            \item All spectral models must be simulated for energies well outside simulation range!
          \end{itemize}
        \item Handled automatically by \roimc
          \begin{itemize}
            \item Parameter \texttt{roi\_pad} (default=2) will pad a given
              amount to energy to every spectral model:
          \end{itemize}
      \end{itemize}
\begin{lstlisting}[language=Python]
actual_emin = simulation_emin/roi_pad
actual_emax = simulation_emax*roi_pad
\end{lstlisting}
\end{frame}
